Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-04 tex/MesnardoBarba2019.tex
add intro passage in section 2

Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.

>>>>

Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
We have learned the hard way how even different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
This section presents an overview and mini-tutorial of the workflow we developed to guarantee the highest level of reproducibility of our computational research, with the best available technology solutions. 
In the process of creating this reproducible workflow, we also evaluated the suitability of public cloud offerings by Microsoft Azure for our research computing needs. 
The tools we adopted for computing on cloud resources are specific for this provider.

To overcome the so-called ``dependency hell'' and facilitate reproducibility and portability, we use the container technology provided by the open-source project Docker.
